---
title: "GuitarModes"
output: github_document
---

```{r setup, include=FALSE}
library(GuitarModes)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Find the positioning of different modes on your guitar. Indicate which chords can be played in the choosen mode/tune and indicate the position of ground notes. Functions defined as R package complemented with a Shiny app for interactive usage. Available at: https://rojorz.shinyapps.io/GuitarModes/

## Installation
Using devtools the package can be installed from github:
   
install.packages("devtools")   
library(devtools)   
install_github("RoJoRZ/GuitarModes")   
   

## Package functionality

The package consist out of several core functions:

Done:

1) GetNote: Get the note from a given posion (with flexible tuning)
2) GetPosition: Get all positions of a certain note (with flexible tuning)
3) GetMode: Get mode positions and tones (at standard tuning)
4) CombineModes: Start with a mode in a tune and get the positions of the other modes 
5) GuitarPlot: Plot Guitar with flexible label size, number of frets, first and last fret to show

Below we give some examples of the core functions

Get a note from a given position:
```{r}
GetNote(string = 1,position = 3)
```

Get positions of a given note:
```{r}
Apositions <- GetPosition("A")
kable(Apositions)
```

Plot on a GuitarPlot
```{r, fig.height= 3, fig.width= 10}
GuitarPlot(Apositions, labsize = 3)
```

Get and plot the Ionian mode in C

```{r, fig.height= 3, fig.width= 10}
Ionian3 <- GetMode(tune = "C",nfrets = 22,mode = "Ionian3")
GuitarPlot(Ionian3, labsize = 3)
```

Get and plot the Ionian mode in A#

```{r, fig.height= 3, fig.width= 10}
Ionian3 <- GetMode(tune = "A#",nfrets = 22,mode = "Ionian3")
GuitarPlot(Ionian3, labsize = 3)
```

Get and plot the Ionian mode in C highlight the target notes (1,3,5) from D. Target 1 = target notes 1,3,5 and target 2 = target notes 1,3,5 and 7. Targetstart is the position of the chord in the base mode.

```{r, fig.height= 3, fig.width= 10}
Ionian3 <- GetMode(tune = "C",nfrets = 22,mode = "Ionian3")
GuitarPlot(Ionian3, labsize = 3, target = 1, targetstart = 2)
```

Get and plot the Ionian mode in C highlight the target notes (1,3,5,7) from E. 

```{r, fig.height= 3, fig.width= 10}
Ionian3 <- GetMode(tune = "C",nfrets = 22,mode = "Ionian3")
GuitarPlot(Ionian3, labsize = 3, target = 2, targetstart = 3)
```

All the above is possible for each church mode: Ionian3, Dorian3, Phrygian3, Lydian3, MixoLydian3, Aeolian3, Locrian3. 
For example get and plot the Phrygian3 mode in E

```{r, fig.height= 3, fig.width= 10}
Phrygian3 <- GetMode(tune = "E",nfrets = 22,mode = "Phrygian3")
GuitarPlot(Phrygian3, labsize = 3)
```

Now it is also possible to combine modes. For example get positions Ionian, Phrygian and Aeolian3 modes starting from C Ionian:

```{r, fig.height= 3, fig.width= 10}
Combine <- CombineModes(tune = "C",basemode = "Ionian3", modes = c("Phrygian3", "Aeolian3"))
GuitarPlot(Combine)
```

Again but now highlighting the target notes from the C7 chord:

```{r, fig.height= 3, fig.width= 10}
Combine <- CombineModes(tune = "C",basemode = "Ionian3", modes = c("Phrygian3", "Aeolian3"))
GuitarPlot(Combine, target = 2, targetstart = 1)
```

Or completely flexible generate any chord or setting in the plot

```{r, fig.height= 3, fig.width= 10}
Ecord <- data.frame(string = c(1,2,3,4,5,6), 
                    position = c(0,2,2,1,0,0), 
                    note = c("E", "B", "E", "G#/Ab","B", "E"))
GuitarPlot(Ecord, nfrets = 4, labsize = 4)
```

