---
title: "GuitarModes"
output: github_document
---

```{r setup, include=FALSE}
library(GuitarModes)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Find the positioning of different modes on your guitar. Indicate which chords can be played in the choosen mode/tune and indicate the position of ground notes. Functions defined as R package complemented with a Shiny app for interactive usage. 


## Package functionality

The package consist out of several core functions:

Done:

1) GetNote: Get the note from a given posion (with flexible tuning)
2) GetPosition: Get all positions of a certain note (with flexible tuning)
3) GetMode: Get mode positions and tones (at standard tuning)
To do:
4) 


X) GuitarPlot: Plot Guitar with flexible label size, number of frets, first and last fret to show

Below we give some examples of the core functions

Get a note from a given position:
```{r}
GetNote(string = 1,position = 3)
```

Get positions of a given note:
```{r}
Apositions <- GetPosition("A")
kable(Apositions)
```

Plot on a GuitarPlot
```{r, fig.height= 3, fig.width= 10}
GuitarPlot(Apositions, labsize = 0)
```

Get and plot the Ionian mode in C

```{r, fig.height= 3, fig.width= 10}
Ionian3 <- GetMode("C", "Ionian3")
GuitarPlot(Ionian3, labsize = 3, firstfret = 5, lastfret = 15)
```


Get and plot the Dorian3 mode in C

```{r, fig.height= 3, fig.width= 10}
Dorian3 <- GetMode("C", "Dorian3")
GuitarPlot(Dorian3, labsize = 3, firstfret = 5, lastfret = 15)
```

Get and plot the Phrygian3 mode in C

```{r, fig.height= 3, fig.width= 10}
Phrygian3 <- GetMode("C", "Phrygian3")
GuitarPlot(Phrygian3, labsize = 3, firstfret = 5, lastfret = 15)
```

Get and plot the Lydian3 mode in C

```{r, fig.height= 3, fig.width= 10}
Lydian3 <- GetMode("C", "Lydian3")
GuitarPlot(Lydian3, labsize = 3, firstfret = 5, lastfret = 15)
```

Get and plot the MixoLydian3 mode in C

```{r, fig.height= 3, fig.width= 10}
MixoLydian3 <- GetMode("C", "MixoLydian3")
GuitarPlot(MixoLydian3, labsize = 3, firstfret = 5, lastfret = 15)
```

Get and plot the Aeolian3 mode in C

```{r, fig.height= 3, fig.width= 10}
Aeolian3 <- GetMode("C", "Aeolian3")
GuitarPlot(Aeolian3, labsize = 3, firstfret = 5, lastfret = 15)
```

Get and plot the Locrian3 mode in C

```{r, fig.height= 3, fig.width= 10}
Locrian3 <- GetMode("C", "Locrian3")
GuitarPlot(Locrian3, labsize = 3, firstfret = 5, lastfret = 15)
```


Or completely flexible generate any chord or setting in the plot

```{r}
Ecord <- data.frame(string = c(1,2,3,4,5,6), 
                    position = c(0,2,2,1,0,0), 
                    note = c("E", "B", "E", "G#/Ab","B", "E"))
GuitarPlot(Ecord, nfrets = 4, labsize = 4)
```

